HPC--101\\Onboarding

### 2016-04-05 hpc_101/paper.tex
updated onboarding sildes to have our directory listed.  Added in the GPU partition to sections we list our partitions out

\author{Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.} % Your name
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

@@

\subsubsection{Hardware}
\begin{frame}
	\frametitle{{\craycs}0 -- Compute Nodes}
	\begin{itemize}
        \item All nodes are diskless with some RAM used for the Operating System
	\item 178 Standard nodes
	  \begin{itemize}
            {\footnotesize
	    \item Two 10 core {\intel} Ivy-Bridge processors (\emph{20 cores total})
	    \item 128GB of physical RAM with $\approx110$GB of useable RAM
            }
	  \end{itemize}

@@

\section{Sustainability}
\subsection{Community Resources}
\begin{frame}
	\frametitle{Community Resources}
	\begin{itemize}
		\item The initial investment in the cluster provides resources for all faculty, staff, and students affiliated with the University of {\hawaii}
		\item All users can run on the publicly accessible partitions:\\ \emph{community.q, exclusive.q, lm.q, sb.q, kill.q, htc.q}
		\item For some users, the publicly available resources may not be enough~\ldots
	\end{itemize}
\end{frame}

@@

\subsubsection{Price Card}
\begin{frame}
	\frametitle{Price Card}
	\begin{center}
	{\large \textbf{Condo Price Card}} \\
	\resizebox{\textwidth}{!}{%
		\begin{tabular}{l r ||l r}
			\toprule
			\textbf{Product} & \textbf{Cost} & \textbf{Product} & \textbf{Cost} \\
			\midrule
			\midrule
			Standard & \$6,600.00  & Standard + 2 GPUs (Nvidia{\regtrademark} K40) & \$13,600.00 \\
			\hline
			Large Memory & \$33,900.00  & 1 TB {\lustre} Storage for 5 years & \$$600.00$ \\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\smallskip
	\begin{center}
		{\large \textbf{Service Unit Price Card}}\\
		\begin{tabular}{l c r }
			\toprule
			\textbf{Product} & \textbf{Cost} & \textbf{Minimum Order}\\
			\midrule
			\midrule
			Standard node & \$0.50 per SU &  1,000~SU (\$500.00)\\
			Large memory node & \$2.00 per SU & 250~SU (\$500.00)\\
			\bottomrule
		\end{tabular}
		\btVFill
	{\footnotesize \emph{All prices are subject to change}}
	\end{center}
\end{frame}

@@

\subsection{Connecting to a cluster @ UH}
\begin{frame}
	\frametitle{Connecting to a cluster @ UH}
	\begin{description}[\setlength{\leftmargini}{0pt}]
	\item[] \begin{itemize}
		\item To connect to the cluster, we utilize a client which communicates using the Secure Shell (\emph{SSH}) protocol 
		\item Linux and MacOSX, typically have a SSH client already installed
		\item Windows typically does not come with an SSH client installed
		\item Windows 10 may come pre-installed with a SSH client, but it might not be stable
		\item Suggested SSH clients for Windows include:
		\begin{itemize}
			\item \href{http://www.hawaii.edu/askus/685}{SSH Secure Shell}~(SSH 3.2.9)
			\item \href{http://www.chiark.greenend.org.uk/~sgtatham/putty/download.html}{Putty}
		\end{itemize}
	\end{itemize}
	\item[] ~\\
	\item[] \begin{itemize}
		\item The {\craycs} has two login nodes:
		\begin{itemize}
			\item uhhpc1.its.hawaii.edu
			\item uhhpc2.its.hawaii.edu
		\end{itemize}
	\end{itemize}
	\end{description}
	{\large Let's attempt to login!}
\end{frame}

@@

\subsection{SLURM Partitions}
\begin{frame}
\footnotesize
\frametitle{Partitions}
\begin{block}{What is a partition?}\footnotesize
A partition can be thought of as a group of nodes/resources divided into possibly overlapping sets.  Each partition can be considered as a job queue, each of which has an assortment of constraints such as job size limit, job time limit, users permitted to use it, etc. Priority-ordered jobs are allocated nodes within a partition until the resources (nodes, processors, memory, etc.) within that partition are exhausted.\footnotemark
\end{block}
\begin{itemize}
	\item The {\craycs} currently has six public partitions:~\\\textbf{lm.q}, \textbf{community.q}, \textbf{exclusive.q}, \textbf{sb.q}, \textbf{kill.q}, \textbf{htc.q}
	\item Jobs submitted to kill.q and htc.q can be preempted by jobs in other partitions
\end{itemize}
\footnotetext[2]{\tiny \url{http://slurm.schedmd.com/quickstart.html}}
\end{frame}

@@

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
%\toprule                                                                    
%\toprule                                                                    
\midrule
\midrule
community.q & \begin{tabular}{l r} \textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} & \padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:}& \padfrom{\ \ \ }{1}~\\ \textbf{Max:}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
\hline
kill.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{12}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
\hline
htc.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
\hline
lm.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ }{262100}\end{tabular}\\
\hline
\hline
sb.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:05:00~\\ \textbf{Max:} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}

>>>>

\author{Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.\\~\\Director\\Gwen Jacobs Ph.D}
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

@@

\subsubsection{Hardware}
\begin{frame}
	\frametitle{{\craycs} -- Compute Nodes}
	\begin{itemize}
        \item All nodes are diskless with some RAM used for the Operating System
	\item 178 Standard nodes
	  \begin{itemize}
            {\footnotesize
	    \item Two 10 core {\intel} Ivy-Bridge processors (\emph{20 cores total})
	    \item 128GB of physical RAM with $\approx110$GB of useable RAM
            }
	  \end{itemize}

@@

\section{Sustainability}
\subsection{Community Resources}
\begin{frame}
	\frametitle{Community Resources}
	\begin{itemize}
		\item The initial investment in the cluster provides resources for all faculty, staff, and students affiliated with the University of {\hawaii}
		\item All users can run on the publicly accessible partitions:\\ \emph{community.q, exclusive.q, lm.q, gpu.q, sb.q, kill.q, htc.q}
		\item For some users, the publicly available resources may not be enough~\ldots
	\end{itemize}
\end{frame}

@@

\subsubsection{Price Card}
\begin{frame}
	\frametitle{Price Card}
	\begin{center}
	{\large \textbf{Condo Price Card}} \\
	\resizebox{\textwidth}{!}{%
		\begin{tabular}{l r ||l r}
			\toprule
			\textbf{Product} & \textbf{Cost} & \textbf{Product} & \textbf{Cost} \\
			\midrule
			\midrule
			Standard & \$6,600.00  & Standard + 2 GPUs (Nvidia{\regtrademark} K40) & \$13,600.00 \\
			\hline
			Large Memory & \$33,900.00  & 1 TB {\lustre} Storage for 5 years & \$$600.00$ \\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\smallskip
	\begin{center}
		{\large \textbf{Service Unit Price Card}}\\
		\begin{tabular}{l || c || r}
			\toprule
			\textbf{Product} & \textbf{Cost} & \textbf{Minimum Order}\\
			\midrule
			\midrule
			Standard node & \$0.50 per SU &  1,000~SU (\$500.00)\\
			Large memory node & \$2.00 per SU & 250~SU (\$500.00)\\
			\bottomrule
		\end{tabular}
		\btVFill
	{\footnotesize \emph{All prices are subject to change}}
	\end{center}
\end{frame}

@@

\subsection{Connecting to a cluster @ UH}
\begin{frame}
	\frametitle{Connecting to a cluster @ UH}
	\begin{description}[\setlength{\leftmargini}{0pt}]
	\item[] \begin{itemize}
		\item To connect to the cluster, we utilize a client which communicates using the Secure Shell (\emph{SSH}) protocol 
		\item Linux and MacOSX, typically have a SSH client already installed
		\item Windows typically does not come with an SSH client installed
		\item Windows 10 may come pre-installed with a SSH client, but it might not be stable
		\item Suggested SSH clients for Windows include:
		\begin{itemize}
			\item \href{http://www.hawaii.edu/askus/685}{SSH Secure Shell}~(SSH 3.2.9)
			\item \href{http://www.chiark.greenend.org.uk/~sgtatham/putty/download.html}{Putty}
                        \item \href{http://mobaxterm.mobatek.net/}{MobaXterm}
		\end{itemize}
	\end{itemize}
	\item[] ~\\
	\item[] \begin{itemize}
		\item The {\craycs} has two login nodes:
		\begin{itemize}
			\item uhhpc1.its.hawaii.edu
			\item uhhpc2.its.hawaii.edu
		\end{itemize}
	\end{itemize}
	\end{description}
	{\large Let's attempt to login!}
\end{frame}

@@

\subsection{SLURM Partitions}
\begin{frame}
\footnotesize
\frametitle{Partitions}
\begin{block}{What is a partition?}\footnotesize
A partition can be thought of as a group of nodes/resources divided into possibly overlapping sets.  Each partition can be considered as a job queue, each of which has an assortment of constraints such as job size limit, job time limit, users permitted to use it, etc. Priority-ordered jobs are allocated nodes within a partition until the resources (nodes, processors, memory, etc.) within that partition are exhausted.\footnotemark
\end{block}
\begin{itemize}
	\item The {\craycs} currently has seven public partitions:~\\\textbf{community.q}, \textbf{exclusive.q}, \textbf{lm.q}, \textbf{gpu.q}, \textbf{sb.q}, \textbf{kill.q}, \textbf{htc.q}
	\item Jobs submitted to kill.q and htc.q can be preempted by jobs in other partitions
\end{itemize}
\footnotetext[2]{\tiny \url{http://slurm.schedmd.com/quickstart.html}}
\end{frame}

@@

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
%\toprule                                                                    
%\toprule                                                                    
\midrule
\midrule
community.q & \begin{tabular}{l r} \textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} & \padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:}& \padfrom{\ \ \ }{1}~\\ \textbf{Max:}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
gpu.q & \begin{tabular}{l r} \textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} & \padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
kill.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{12}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
htc.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
lm.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
sb.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:05:00~\\ \textbf{Max:} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}
